### 2024-04-16 README.Rmd
hex position on readme
with adjust col seq for st_augment
minor alteration
add arxiv link to readme

<!-- README.md is generated from README.Rmd. Please edit that file -->

@@

<img src="man/figures/logo.png" align="right" height="240"/>

# sfislands

@@

@@

Install the released version from CRAN

>>>>

@@

# sfislands <img src="man/figures/logo.png" align="right" height="240"/>

<!-- badges: start -->
<!-- badges: end -->

@@

A pre-print of a paper discussing the package is available [here](https://arxiv.org/abs/2404.09863).

@@

Install the released version from CRAN:
